### 2016-02-24 FCCreport/HH4b.tex
FCC report

J. Katharina Behr, Daniela Bortoletto, James A. Frost,\\
  Nathan P. Hartland, Cigdem Issever and Juan Rojo

\vspace{.3cm}
{\it Physics Department, 1 Keble Road, University of Oxford, United Kingdom }

@@

In this contribution we provide an estimate of the accuracy
in the Higgs self-coupling extraction that can be achieved at a 100 TeV
hadron collider in the  $b\bar{b}b\bar{b}$ final state.
%
The analysis methodology is based on our feasibility
study at 14 TeV~\cite{Behr:2015oqq}, with suitable modifications for the 100 TeV
case.
%
This strategy is based upon a combination of traditional cut-based
 methods and Multivariate Analysis (MVA).
  %
  We account for  all relevant
  backgrounds, including the contribution from mis-identified
  light and charm jets.
  %
  Our analysis strategy is found to be robust even in a high pile-up
  environment.
  %
 Our results at 14 TeV~\cite{Behr:2015oqq} indicate that 
  the $b\bar{b}b\bar{b}$ 
final state
alone should allow for the observation of double Higgs production
  at the HL-LHC, and here we study how our findings apply to the case of a 100
  TeV collider.
  %
  Other studies of Higgs pair production in the same
final state can be found in Refs.~\cite{Wardrope:2014kya,deLima:2014dta}.

@@

Higgs pair production in the gluon-fusion
channel is simulated at leading order (LO) using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca,Maltoni:2014eza}
using a tailored  model
which includes mass effects
from the
exact form factors.
%
The calculation is performed in the
$n_f$=4 scheme and
the renormalization and factorization
scales are taken to be $\mu_F=\mu_R=H_T/2$.
%
For the input PDFs we 
adopt the NNPDF 3.0 $n_f=4$ LO set~\cite{Ball:2014uwa} with
$\alpha_s(m_Z^2)=0.118$,
interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
%
To achieve the correct higher-order value of the
integrated cross-section, we rescale our LO signal sample to match the
NNLO+NNLL
inclusive calculation~\cite{deFlorian:2013jea,deFlorian:2015moa}.
%
Parton level signal events are then showered with the {\tt Pythia8} Monte
Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea}, version {\tt v8.201},
using the  Monash 2013 tune~\cite{Skands:2014pea},
based on the NNPDF2.3LO PDF set~\cite{Ball:2012cx,Ball:2013hta}.
%
Background samples are generated at LO
with {\tt SHERPA}~\cite{Gleisberg:2008ta} {\tt v2.1.1}
and rescaled to known higher-order results.
%
The input PDFs and scales are the same as for
the signal samples.
%
In this study we include the irreducible QCD $4b$ background
as well as the reducible $2b2j$ component, since the $4j$ processes
is shown to be negligible.
%
We also include top quark pair
production.
%
Single Higgs production processes and electroweak backgrounds
are much smaller and not included here.
%

\paragraph{Analysis strategy.}
After the parton shower, final state particles
are clustered using the
jet reconstruction algorithms
of
{\tt FastJet}~\cite{Cacciari:2011ma,Cacciari:2005hq},
{\tt v3.1.0}.
%
First of all, we define {\it small-$R$ jets}, reconstructed with the
anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with $R=0.4$,
and  required
  to have transverse momentum $p_T \ge 40$~GeV
  and pseudo-rapidity $|\eta|<2.5$.
  %
  The we also define {\it large-$R$ jets},  reconstructed with 
  anti-$k_T$ with $R=1.0$, and
   required to have
  $p_T \ge 200$~GeV, lie in the
  $|\eta|<2.0$ region and
   satisfy the  BDRS mass-drop tagger (MDT)~\cite{Butterworth:2008iy}.
   %
   Finally, we define
  {\it small-$R$ subjets}, constructed  
  by clustering all final-state particles with
 anti-$k_T$ with  $R=0.3$, that are then
 ghost-associated  to the large-$R$ jets~\cite{Aad:2015uka}.
 %
 These
  are required to satisfy
  $p_T > 50$~GeV and $|\eta|<2.5$.
  %
  Our cuts are deliberately loose since their optimization will be
  performed at the MVA level.
%
For the   boosted and intermediate categories,
which involve large-$R$ jets,
we also use a number of jet substructure variables~\cite{Salam:2009jx,Aad:2013gja}:
the $k_T$-splitting scale~\cite{Butterworth:2002tt,Butterworth:2008iy}, the ratio of 2-to-1 subjettiness $\tau_{21}$~\cite{Thaler:2010tr,Thaler:2011gf}, and the ratios of energy correlation functions (ECFs)  $C^{(\beta)}_2$~\cite{Larkoski:2013eya} and
$D_2^{(\beta)}$~\cite{Larkoski:2014gra}.

For each jet definition described above, a different
$b$-tagging strategy is adopted.
%
For  {\it small-$R$ jets}, if it contains at least one $b$-quark among its constituents,
it will be tagged as a $b$-jet with probability $f_b$, provided
the $p_T$ of the $b$-quark
  satisfies $p_T \ge 15$ GeV~\cite{Aad:2015ydr}.
  %
  If no $b$-quarks are found among the constituents
  of this jet, it can be still be tagged as a $b$-jet with
  a mistag rate of $f_l$, provided it has at least one
  constituent
  with $p_T \ge 15$ GeV.
  %
 For {\it large-$R$ jets} instead, they are $b$-tagged by
    ghost-associating anti-$k_T$ $R=0.3$ (AKT03)
    subjets to the original large-$R$
    jets~\cite{Cacciari:2007fd,Aad:2013gja,
      ATLAS-CONF-2014-004,Aad:2015uka}.
    %
    A large-$R$ jet is considered $b$-tagged if both
    the leading and subleading AKT03 subjets are both individually $b$-tagged,
    with the same criteria as the small-$R$ jets.
    %
     The treatment of the $b$-jet mis-identification
    from light and charm jets
    is the same as for the small-$R$ jets.
  %
For the $b$-tagging probability $f_b$, along with
the $b$-mistag probability of light ($f_l$) and charm ($f_c$) jets,
we use the values $f_b=0.8$, $f_l=0.01$
and  $f_c=0.1$.

Our analysis strategy follows the
scale-invariant resonance tagging method of Ref.~\cite{Gouzevitch:2013qca}.
%
Rather than restricting to a specific event topology,
we consistently combine the information from
the three possible topologies: boosted, intermediate and
resolved, with the optimal cuts for each category being determined
separately.
%
The three categories are defined as follows.
%
Events are classified in the {\it boosted category} if they 
  contain at least two large-$R$ jets, with the two leading jets
  being $b$-tagged.
  %
  They will be classified in the
 {\it intermediate category} if there is exactly one  $b$-tagged, large-$R$ jet, which
  is assigned to be the leading Higgs candidate.
  %
  In addition, we require at least two $b$-tagged, small-$R$ jets,
  which must be separated with respect to the large-$R$ jet
  by  $\Delta R\ge 1.2$.
  %
  Finally, events will be assigned to the {\it resolved category}
  if they contain at least
  four $b$-tagged small-$R$ jets.
  %
  The two Higgs candidates are reconstructed out of the
  leading four small-$R$ jets in the event by minimizing the relative difference of
  dijet masses.
  %
  In all categories, once a Higgs boson candidate has been identified,
its invariant mass is required to lie within a fixed window
of width $80~{\rm GeV}$ around the nominal Higgs boson mass of $m_h= 125$
GeV.
%

\paragraph{Results.}
As discussed in~\cite{Behr:2015oqq}, at the end of the cut-based
analysis, events are processed with an MVA to optimise
the separation between signal and backgrounds.
%
The specific type of  MVA that we use is
a multi-layer feed-forward artificial neural network (ANN),
known as {\it perceptrons} or {\it deep neural networks}.
%
The MVA inputs are the set of kinematic variables describing the
signal and background
events which satisfy the requirements of the
cut-based analysis, including the jet substructure variables.
%
The output of the trained ANNs allows for the identification,
in a fully automated way,
of the most relevant variables for the discrimination between 
signal and background.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{|c|l|c|c|c|c|}
    \hline
    \multicolumn{6}{|c|}{FCC100, $\mathcal{L}=10$ ab$^{-1}$} \\
    \hline
    \hline
    Category  &   &  $N_{\rm ev}$ signal &  $N_{\rm ev}$ back  &  $S/\sqrt{B}$ & $S/B$ \\ 
    \hline
    \hline
    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  &       $5\cdot 10^4$    &   $8\cdot 10^7$        &  6        &    $6\cdot 10^{-4}$         \\
    &  $y_{\rm cut}=0.99$ &   $2\cdot 10^4$    &  $1\cdot 10^6$         &      22    &    0.02     \\
    \hline
    \hline
    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  &   $3\cdot 10^4$     & $1\cdot 10^8$  & 3   &  $3\cdot 10^{-4}$ \\
       &  $y_{\rm cut}=0.98$ &         $2\cdot 10^4$       &  $2\cdot 10^6$   &  10   & 0.007         \\
    \hline
    \hline
      \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  &  $1\cdot 10^5$      & $8\cdot 10^8$  &   4  & $1.0\cdot 10^{-4}$  \\
    &  $y_{\rm cut}=0.95 $ &    $6\cdot 10^4$    &   $2\cdot 10^7$        &    15      &    0.004     \\
    \hline
      \end{tabular}
  \caption{\small Post-MVA results, for the optimal value of the
    ANN discriminant $y_{\rm cut}$ in the three categories, compared with the
    corresponding
    pre-MVA results ($y_{\rm cut}=0$).
    %
    We quote the number of signal and
    background events expected for $\mathcal{L}=10$ ab$^{-1}$,
    the signal significance $S/\sqrt{B}$ and
    the signal over background ratio $S/B$.
    %
    Only the QCD $4b$ background is considered here.
    %
    \label{table:cutflowMVA}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

From Fig.~\ref{fig:sb_mva} and Table~\ref{table:cutflowMVA} we observe that the statistical
significance of the three categories is very large, with a post-MVA value of
$S/\sqrt{B}\simeq 20$ in the boosted
category.
%
However, we also find that as compared to 14 TeV, the QCD multijet background increases
more rapidly than the signal, and thus $S/B$ is actually smaller than at 14 TeV~\cite{Behr:2015oqq}.
%
Achieving  percent values in $S/B$ requires a very hard cuts on the value of the ANN output.
%
We observe that at 100 TeV the boosted category is the most promising one: not only
it benefits from the highest signal significances, it also exhibits
the best signal over background ratio.
%
Let us recall that at 14 TeV instead~\cite{Behr:2015oqq}  the higher significance was obtained with the resolved category.
%
Unfortunately, as we discuss below, the boosted category is the less sensitive to the Higgs self-coupling,
and thus a measurement of the trilinear will depend to good extent on the resolved category.
%
Therefore, at a 100 TeV collider, even more that at 14 TeV, the feasibility of the measurement
of $\sigma(hh\to b\bar{b}b\bar{b})$ depends strongly on how small the systematic
uncertainties can be, in particular for the background determination.

@@

  The sensitivity in the Higgs self-coupling is defined by the $\chi^2$ estimator
  \be
  \label{eq:chi2profile}
  \chi^2(\lambda) \equiv \frac{\lc \sigma(hh,\lambda) - \sigma(hh,\lambda_{\rm SM})
    \rc^2}{\lp \delta_{\rm stat}\sigma\rp^2+\lp \delta_{\rm sys}\sigma\rp^2 } \, ,
  \ee
  where $\lambda$ is the Higgs
  self-coupling, $\lambda_{\rm SM}$ is the SM value, $\sigma(hh,\lambda)$ is the
  post-MVA signal cross-section for a given value of $\lambda$, and $\delta_{\rm stat}\sigma$ and
  $\delta_{\rm sys}\sigma$ are respectively the statistical and systematic uncertainties in the cross-section
  measurement.
  %
  Signal samples for a range of $\lambda$ values have been  processed
  by the same analysis chain, including the MVA (which is not
  retrained), than the SM samples.
  %
  The 68\% CL range for the extraction of $\lambda$ can then be found using
  the usual parameter-fitting criterion by determining the values $\pm \delta\lambda$
  for which the cross-section satisfies
  \be
  \label{eq:condition}
\chi^2(\lambda_{\rm SM}~^{+\delta\lambda}_{-\delta\lambda})=\chi^2(\lambda_{\rm SM})+1 \, .
\ee
%
The final result for the accuracy in the trilinear extraction can be obtained by combining
in quadrature the separate results
from the three exclusive categories.

In Fig.~\ref{fig:chi2} we show the $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section at
  various steps of the cut-flow, including after $b$-tagging
  (before MVA) and after the MVA, in the resolved (left plot)
  and boosted (right plot) categories,  as a function of the Higgs self-coupling
  $\lambda/\lambda_{\rm SM}$ in units of the SM coupling.
  %
  See~\cite{Behr:2015oqq} for the definition of the different steps
  in the analysis chain.
  %
  We find that, despite that fact that the MVA is only trained on the SM sample, the signal
  selection efficiency of the MVA is relatively flat when $\lambda$ is varied, reflecting the fact
  that the signal kinematics do not change dramatically.
  %
  We also see that the resolved category (low and medium Higgs $p_T$) is more sensitive to variations of $\lambda$ than
  the boosted one (large Higgs $p_T$), as indicated by the shallower minimum of the latter after the MVA.
  %
  This reflects the well-known fact that the triangle diagram (which depends on the Higgs self-coupling) is
  dominant near the threshold region.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.48\textwidth]{plots/res_xSec_100TeV.pdf}
\includegraphics[width=0.48\textwidth]{plots/bst_xSec_100TeV.pdf}
\caption{\small
  The $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section at
  various steps of the cut-flow, including after $b$-tagging
  (before MVA) and after the MVA, in the resolved (left plot)
  and boosted (right plot) categories, as  as a function of the Higgs self-coupling
  $\lambda/\lambda_{\rm SM}$ in units of the SM coupling.
}
\label{fig:chi2}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

 %
  Imposing the condition Eq.~(\ref{eq:condition}) we can derive the 68\% confidence level intervals
  on the Higgs self-coupling $\lambda_{\rm min}/\lambda_{\rm SM}$ (in units of the SM value) in the boosted, resolved and intermediate categories, for  different assumptions on the total systematic error in the measured
  cross-section.
  %
  The ranges that are found are reported in Table~\ref{tab:chi2}.
  %
  As expected, the results depend very strongly on the assumption for the systematic uncertainty
  on the measured cross-section.
  %
  In the optimistic scenario of a measurement with $\delta_{\rm sys}\sigma=25\%$,
  the best performance comes from the resolved category, where at the 68\% CL the trilinear
  can be determined to lie in the interval $\lambda/\lambda_{SM}\in \lc 0.9, 1.5\rc$.
  %
  Looser constrains are derived from the intermediate and specially from the boosted category.
  %
  On the other hand, for $\delta_{\rm sys}\sigma=100\%$, the constraints in all three categories
  become very loose, specially for $\lambda/\lambda_{\rm SM}\ge 1$, due to the negative interference effects.

@@

\paragraph{Summary.} In this contribution we have performed a first exploration of the accuracy that can be expected
for the extraction of the Higgs self-coupling at a 100 TeV hadron collider using the $b\bar{b}b\bar{b}$ final state.
%
We find that while the statistical significance of the measurement of the $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section
is very large, the $S/B$ ratio is quite low (and in particular worse than at 14 TeV),
specially in the resolved category, the one with the highest sensitivity
to the self-coupling.
%
This is a consequence of the fact that from 14 TeV to 100 TeV the QCD multijet background increases more rapidly than
the di-Higgs signal.
%
Our estimate of the expected precision on the Higgs trilinear depends strongly on the assumptions
about the experimental systematics.
%
For a measurement with a 25\% systematic uncertainty, the self-coupling can be determined
with accuracy $^{+50\%}_{-10\%}$ at the 68\% CL using the resolved category, but these constraints become substantially
looser if the systematic uncertainties are increased.

>>>>

J. Katharina Behr$^{1,2}$, Daniela Bortoletto$^1$, James A. Frost$^1$,\\[0.1cm]
  Nathan P. Hartland$^1$, Cigdem Issever$^1$, and Juan Rojo$^1$

\vspace{.3cm}
       {\it ~$^1$ Physics Department, 1 Keble Road, University of Oxford, United Kingdom. \\[0.1cm]
       ~$^2$ Deutsches Elektronen-Synchrotron (DESY),
Notkestrasse 85, D-22607 Hamburg,
Germany.}

@@

In this contribution we provide a first estimate of the accuracy
in the Higgs self-coupling extraction that can be achieved at a 100 TeV
hadron collider in the  $b\bar{b}b\bar{b}$ final state.
%
The analysis methodology is based on our recent feasibility
study at 14 TeV~\cite{Behr:2015oqq}, with suitable modifications for the 100 TeV
case.
%
This strategy is based upon a combination of traditional cut-based
 methods and Multivariate Analysis (MVA).
 %
 In our 14 TeV study~\cite{Behr:2015oqq},  we accounted for  all relevant
  backgrounds, including the contribution from mis-identified
  light and charm jets, and showed that our
  analysis strategy was robust even in a high pile-up (PU)
  environment.
  %
 Our results indicate that 
  the $b\bar{b}b\bar{b}$ 
final state
alone should allow for the observation of double Higgs production
at the HL-LHC.
%
Here we study how our findings apply to the case of a 100
TeV collider.
%
For simplicity, we will consider only the irreducible
QCD $4b$ background, and present results for the simulations without PU.
  %
  Other studies of Higgs pair production in the same
final state can be found in Refs.~\cite{Wardrope:2014kya,deLima:2014dta}.

@@

Higgs pair production in the gluon-fusion
channel is simulated at leading order (LO) using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca,Maltoni:2014eza}
using the recently developed functionalities for
loop-induced processes~\cite{Hirschi:2015iia}.
%
The calculation is performed in the
$n_f$=4 scheme and
the renormalization and factorization
scales are taken to be $\mu_F=\mu_R=H_T/2$.
%
For the input PDFs we 
adopt the NNPDF 3.0 $n_f=4$ LO set~\cite{Ball:2014uwa} with
$\alpha_s(m_Z^2)=0.118$,
interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
%
To achieve the correct higher-order value of the
integrated cross-section, we rescale our LO signal sample to match the
NNLO+NNLL
inclusive calculation~\cite{deFlorian:2013jea,deFlorian:2015moa}.
%
Parton level signal events are then showered with
{\tt Pythia8}~\cite{Sjostrand:2007gs,Sjostrand:2014zea}, version {\tt v8.201},
using the  Monash 2013 tune~\cite{Skands:2014pea},
based on the NNPDF2.3LO PDF set~\cite{Ball:2012cx,Ball:2013hta}.
%
Background samples are generated at LO
with {\tt SHERPA}~\cite{Gleisberg:2008ta} {\tt v2.1.1}
and rescaled to known higher-order results, using
the same $K$-factors as in~\cite{Behr:2015oqq}. 
%
The input PDFs and scales are the same as for
the signal samples.
%
In order to provide an estimate of signal significance at 100 TeV,
we shall consider in this
contribution only the irreducible QCD $4b$ background.
%
Single Higgs production processes and electroweak backgrounds
are much smaller and are also not included here.
%

\paragraph{Analysis strategy.}
After the parton shower, final state particles
are clustered using the
jet reconstruction algorithms
of
{\tt FastJet}~\cite{Cacciari:2011ma,Cacciari:2005hq},
{\tt v3.1.0}.
%
First of all, we reconstruct {\it small-$R$ jets} with the
anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with $R=0.4$,
and  require them
  to have transverse momentum $p_T \ge 40$~GeV
  and pseudo-rapidity $|\eta|<2.5$.
  %
  We also define {\it large-$R$ jets},  reconstructed with 
  anti-$k_T$ with $R=1.0$.
  %
  These
 are
   required to have
  $p_T \ge 200$~GeV, lie in the
  $|\eta|<2.0$ region and
   satisfy the  BDRS mass-drop tagger (MDT)~\cite{Butterworth:2008iy}.
   %
   Finally, we define
  {\it small-$R$ subjets}, constructed  
  by clustering all final-state particles with
 anti-$k_T$ with  $R=0.3$, that are then
 ghost-associated  to the large-$R$ jets~\cite{Aad:2015uka}.
 %
 These
  are required to satisfy
  $p_T > 50$~GeV and $|\eta|<2.5$.
  %
For the   boosted and intermediate categories,
which involve large-$R$ jets,
we also use a number of jet substructure variables~\cite{Salam:2009jx,Aad:2013gja}:
the $k_T$-splitting scale~\cite{Butterworth:2002tt,Butterworth:2008iy}, the ratio of 2-to-1 subjettiness $\tau_{21}$~\cite{Thaler:2010tr,Thaler:2011gf}, and the ratios of energy correlation functions (ECFs)  $C^{(\beta)}_2$~\cite{Larkoski:2013eya} and
$D_2^{(\beta)}$~\cite{Larkoski:2014gra}.

For each jet definition a different
$b$-tagging strategy is adopted.
%
For a {\it small-$R$ jet}, if it contains at least one $b$-quark among its constituents,
it will be tagged as a $b$-jet with probability $f_b$, provided
the $p_T$ of the $b$-quark
  satisfies $p_T \ge 15$ GeV~\cite{Aad:2015ydr}.
  %
  If no $b$-quarks are found among the constituents
  of this jet, it can be still be tagged as a $b$-jet with
  a mistag rate of $f_l$, provided it has at least one
  constituent
  with $p_T \ge 15$ GeV, unless this constituent
  is a charm quark, and then the mistag rate is instead $f_c$.
  %
 {\it Large-$R$ jets} are $b$-tagged by
    ghost-associating anti-$k_T$ $R=0.3$ (AKT03)
    subjets to the original large-$R$
    jets~\cite{Cacciari:2007fd,Aad:2013gja,
      ATLAS-CONF-2014-004,Aad:2015uka}.
    %
    A large-$R$ jet is considered $b$-tagged if both
    the leading and subleading AKT03 subjets are both individually $b$-tagged,
    with the same criteria as the small-$R$ jets.
    %
     The treatment of the $b$-jet mis-identification
    from light and charm jets
    is the same as for the small-$R$ jets.
  %
For the $b$-tagging probability $f_b$, along with
the $b$-mistag probability of light ($f_l$) and charm ($f_c$) jets,
we use the values $f_b=0.8$, $f_l=0.01$
and  $f_c=0.1$.

Our analysis strategy follows the
scale-invariant resonance tagging method of Ref.~\cite{Gouzevitch:2013qca}.
%
Rather than restricting to a specific event topology,
we consistently combine the information from
the three possible topologies: boosted, intermediate and
resolved, with the optimal cuts for each category being determined
separately.
%
The three categories are defined as follows.
%
Events are classified in the {\it boosted category} if they 
  contain at least two large-$R$ jets, with the two leading jets
  being $b$-tagged.
  %
  They will be classified in the
 {\it intermediate category} if there is exactly one  $b$-tagged, large-$R$ jet, which
  is assigned to be the leading Higgs candidate.
  %
  In addition, we require at least two $b$-tagged, small-$R$ jets,
  which must be separated with respect to the large-$R$ jet
  by  $\Delta R\ge 1.2$.
  %
  Finally, events will be assigned to the {\it resolved category}
  if they contain at least
  four $b$-tagged small-$R$ jets.
  %
  The two Higgs candidates are reconstructed out of the
  leading four small-$R$ jets in the event by minimizing the relative difference of
  dijet masses.
  %
  In all categories, once a Higgs boson candidate has been identified,
its invariant mass is required to lie within a fixed window
of width $80~{\rm GeV}$,
symmetric around the nominal Higgs boson mass of $m_h= 125$
GeV.
%
 Our object and event selection are deliberately loose since their optimization will be
  performed at the MVA level.

\paragraph{Results.}
As discussed in~\cite{Behr:2015oqq}, at the end of the cut-based
analysis, events are processed with an MVA to optimise
the separation between signal and backgrounds.
%
The specific type of  MVA that we use is
a multi-layer feed-forward artificial neural network (ANN),
known as {\it perceptron} or {\it deep neural network}.
%
The MVA inputs are the set of kinematic variables describing the
signal and background
events which satisfy the requirements of the
cut-based analysis, including the jet substructure variables.
%
The output of the trained ANNs allows for the identification,
in a fully automated way,
of the most relevant variables for the discrimination between 
signal and background.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{|c|l|c|c|c|c|}
    \hline
    \multicolumn{6}{|c|}{FCC100, $\mathcal{L}=10$ ab$^{-1}$} \\
    \hline
    \hline
    Category  &   &  $N_{\rm ev}$ signal &  $N_{\rm ev}$ back  &  $S/\sqrt{B}$ & $S/B$ \\ 
    \hline
    \hline
    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  &       $5\cdot 10^4$    &   $8\cdot 10^7$        &  6        &    $6\cdot 10^{-4}$         \\
    &  $y_{\rm cut}=0.99$ &   $2\cdot 10^4$    &  $1\cdot 10^6$         &      22    &    $2\cdot 10^{-2}$     \\
    \hline
    \hline
    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  &   $3\cdot 10^4$     & $1\cdot 10^8$  & 3   &  $3\cdot 10^{-4}$ \\
       &  $y_{\rm cut}=0.98$ &         $2\cdot 10^4$       &  $2\cdot 10^6$   &  10   & $7\cdot 10^{-3}$        \\
    \hline
    \hline
      \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  &  $1\cdot 10^5$      & $8\cdot 10^8$  &   4  & $1\cdot 10^{-4}$  \\
    &  $y_{\rm cut}=0.95 $ &    $6\cdot 10^4$    &   $2\cdot 10^7$        &    15      &    $4\cdot 10^{-3}$     \\
    \hline
      \end{tabular}
  \caption{\small Post-MVA results, for the optimal value of the
    ANN discriminant $y_{\rm cut}$ in the three categories, compared with the
    corresponding
    pre-MVA results ($y_{\rm cut}=0$).
    %
    We quote the number of signal and
    background events expected for $\mathcal{L}=10$ ab$^{-1}$,
    the signal significance $S/\sqrt{B}$ and
    the signal over background ratio $S/B$.
    %
    In this table, only the irreducible
    QCD $4b$ background has been considered.
    %
    \label{table:cutflowMVA}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

From Fig.~\ref{fig:sb_mva} and Table~\ref{table:cutflowMVA} we observe that the statistical
significance of the three categories is very large, with a post-MVA value of
$S/\sqrt{B}\simeq 20$ in the boosted
category.
%
However, we also find that as compared to 14 TeV, the QCD
$4b$ multijet background increases
more rapidly than the signal, and thus $S/B$ is actually smaller than at 14 TeV~\cite{Behr:2015oqq}.
%
Achieving  percent values in $S/B$ requires very hard cuts on the value of the ANN output $y_{\rm cut}$.
%
We observe that at 100 TeV the boosted category is the most promising one: not only
it benefits from the highest signal significances, it also exhibits
the best signal over background ratio.
%
Let us recall that at 14 TeV~\cite{Behr:2015oqq} the  significance
of the three categories was quite similar, with the boosted one being the best without PU, and
the resolved one
exhibiting the higher significance in the simulations with PU.
%
Unfortunately, as we discuss below, the boosted category is the less sensitive to the Higgs self-coupling,
and thus a measurement of the trilinear will depend to good extent on the resolved category.
%
The smallness of $S/B$ indicates that
at a 100 TeV collider, even more that at 14 TeV, the feasibility of the measurement
of the $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section
will depend strongly on how small the systematic
uncertainties will be, in particular those associated to the background determination.

@@

  The sensitivity in the Higgs self-coupling is defined by the $\chi^2$ estimator
  \be
  \label{eq:chi2profile}
  \chi^2(\lambda) \equiv \frac{\lc \sigma(hh,\lambda) - \sigma(hh,\lambda_{\rm SM})
    \rc^2}{\lp \delta_{\rm stat}\sigma\rp^2+\lp \delta_{\rm sys}\sigma\rp^2 } \, ,
  \ee
  where $\lambda$ is the Higgs
  self-coupling, $\lambda_{\rm SM}$ is the SM value, $\sigma(hh,\lambda)$ is the
  post-MVA signal cross-section for a given value of $\lambda$, and $\delta_{\rm stat}\sigma$ and
  $\delta_{\rm sys}\sigma$ are respectively the statistical and systematic uncertainties in the cross-section
  measurement.
  %
  Signal samples for a range of $\lambda$ values have been  processed
  by the same analysis chain, including the MVA (which is not
  retrained), as the SM samples.
  %
  The 68\% CL range for the extraction of $\lambda$ can then be found using
  the usual parameter-fitting criterion to determine the values $\pm \delta\lambda$
  for which the cross-section satisfies
  \be
  \label{eq:condition}
\chi^2(\lambda_{\rm SM}~^{+\delta\lambda}_{-\delta\lambda})=\chi^2(\lambda_{\rm SM})+1 \, .
\ee
%

In Fig.~\ref{fig:chi2} we show the
 $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section at
  various steps of the cut-flow: generator level, after
  kinematical cuts~\cite{Behr:2015oqq}, after $b$-tagging
  and finally after the MVA.
  %
  We show the results
  in the resolved (left plot)
  and boosted (right plot) categories,
  as  as a function of the Higgs self-coupling
  $\lambda/\lambda_{\rm SM}$ in units of the SM coupling.
  %
  For the MVA cut,  a representative value of $y_{\rm cut}\simeq 0.7$
  has been used.
  %
  We find that, despite that fact that the MVA is only trained on the SM sample, the signal
  selection efficiency of the MVA is relatively flat when $\lambda$ is varied, reflecting the fact
  that the signal kinematics do not change dramatically.
  %
  We also see that the resolved category (low and medium Higgs $p_T$) is more sensitive to variations of $\lambda$ than
  the boosted one (large Higgs $p_T$), as indicated by the shallower minimum of the latter after
  the $b$-tagging and MVA cuts.
  %
  This reflects the fact that the triangle diagram (which depends on the Higgs self-coupling) is
  dominant near the threshold region.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.48\textwidth]{plots/res_xSec_100TeV.pdf}
\includegraphics[width=0.48\textwidth]{plots/bst_xSec_100TeV.pdf}
\caption{\small
  The $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section at
  various steps of the cut-flow: generator level, after
  kinematical cuts, after $b$-tagging
  and finally after the MVA.
  %
  We show the results
  in the resolved (left plot)
  and boosted (right plot) categories,
  as  as a function of the Higgs self-coupling
  $\lambda/\lambda_{\rm SM}$ in units of the SM coupling.
  %
  For the MVA, a representative value of the ANN output of $y_{\rm cut}\simeq 0.7$
  has been used in this plot.
}
\label{fig:chi2}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

 %
  Imposing the condition Eq.~(\ref{eq:condition}) we can derive the 68\% confidence level intervals
  on the Higgs self-coupling $\lambda_{\rm min}/\lambda_{\rm SM}$ (in units of the SM value) in the boosted, resolved and intermediate categories, for  different assumptions on the total systematic error in the measured
  cross-section.
  %
  The ranges that are found are reported in Table~\ref{tab:chi2}.
  %
  As expected, the results depend
  strongly on the assumption for the systematic uncertainty
  on the measured cross-section.
  %
  In the optimistic scenario of a measurement with $\delta_{\rm sys}\sigma=25\%$,
  the best performance comes from the resolved category, where at the 68\% CL the trilinear
  can be determined to lie in the interval $\lambda/\lambda_{\rm SM}\in \lc 0.9, 1.5\rc$.
  %
  Looser constrains are derived from the intermediate and specially from the boosted category.
  %
  On the other hand, for $\delta_{\rm sys}\sigma=100\%$, the constraints in all three categories
  degrade substantially, specially for $\lambda/\lambda_{\rm SM}\ge 1$, due to the negative interference effects.

@@

\paragraph{Summary.} In this contribution we have performed a first exploration of the accuracy that can be expected
for the extraction of the Higgs self-coupling at a 100 TeV hadron collider using the $b\bar{b}b\bar{b}$ final state.
%
We find that while the statistical significance of the measurement of the $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section
is very large, the $S/B$ ratio is quite low (and in particular worse than at 14 TeV),
specially in the resolved category, the one with the highest sensitivity
to the self-coupling.
%
Our estimate of the expected precision on the Higgs trilinear thus depends strongly on the assumptions
about the experimental systematic uncertainty.
%
For a measurement with a 25\% systematic uncertainty, the self-coupling can be determined
with accuracy $^{+50\%}_{-10\%}$ at the 68\% CL using the resolved category, but these constraints become substantially
looser if the systematic uncertainties are increased.
